\Large {\bf rt1d: Documentation}

### 2012-05-22 doc/manual/rt1d_manual.tex
Added script to compare optimal monochromatic and effective column density solutions to RT06 #2.

\usepackage{amsmath, amsthm, amssymb}
\numberwithin{equation}{section}
\usepackage{graphicx}
\usepackage{pslatex}
\usepackage{epsfig}
\usepackage{natbib}
\usepackage[pdfborder={0 0 0}]{hyperref}
\usepackage[all]{hypcap}

@@

%%%
%% Introduction
%%%
\section{Introduction}
Let's see what happens to the gas around stars and black holes, shall we? The
primary reference for this code is
\href{http://arxiv.org/abs/1204.1944}{arxiv:1204.1944} -- much of the text has
been extracted from there.

@@

% Secondary Electrons
\subsection{Additional Complexity: Energy Dependent Secondary Electron Treatment}
In the previous section (and in all of \citet{Mirocha2012}), we considered the asymptotic limit of \citet{Shull1985}, in which the fractional energy deposition of secondary electrons as heat, ionization, and excitation depends only on the hydrogen ionized fraction.  \citet{Furlanetto2010} updated this work, providing lookup tables of deposition fraction as a function of both ionized fraction and electron energy.  These effects are most important at $E \lesssim 10^2$ eV.

@@

We must also modify the minimum and maximum column densities for our integral tables.  To calculate what these should be for a simulation spanning the redshift interval $(z_i, z_f)$, minimum species fraction $x_{\mathrm{min}}$, and grid resolution (in proper coordinates) $dx$, do
\begin{align}
    N_{\HI}^{\mathrm{min}} & = \bar{n}_H^0 (1 + z_f)^3 dx x_{\mathrm{min}}   \\
    N_{\HI}^{\mathrm{max}} & = \bar{n}_H^0 (1 + z_i)^3 \Lbox .
\end{align}

@@

%%%
%% Advanced usage
%%%
\section{Advanced Usage}

>>>>

\usepackage{amsmath, amsthm, amssymb}
\numberwithin{equation}{section}
\usepackage{graphicx}
\usepackage{pslatex}
\usepackage{epsfig}
\usepackage{natbib}
\usepackage[pdfborder={0 0 1}]{hyperref}

@@

%%%
%% Introduction
%%%
\section{Introduction}
Let's see what happens to the gas around stars and black holes, shall we? The
primary reference for this code is \cite[\href{http://arxiv.org/abs/1204.1944}{arxiv:1204.1944}]{Mirocha2012} -- much of the text has
been extracted from there.

@@

% Secondary Electrons
\subsection{Additional Complexity: Energy Dependent Secondary Electron Treatment}
In the previous section (and in all of \citet{Mirocha2012}), we considered the asymptotic limit of \citet{Shull1985}, in which the fractional energy deposition of secondary electrons as heat, ionization, and excitation depends only on the hydrogen ionized fraction.  \citet{Ricotti2002} and \citet{Furlanetto2010} updated this work, providing (respectively) empirical fits and lookup tables of deposition fraction as a function of both ionized fraction and electron energy. These effects are most important at $E \lesssim 10^2$ eV.

@@

Let's first account for dilution of ion densities by expansion.  The number density of atoms at the cosmic mean density evolves as
\begin{align}
    \frac{dn}{dt} & = \frac{dn}{dz}\frac{dz}{dt} \nonumber \\
    & = \frac{d}{dz}\left(\bar{n}^0 (1 + z)^3 \right) \frac{dz}{dt} \nonumber \\
    & = 3 \bar{n}^0 (1 + z)^2 \frac{dz}{dt} .
\end{align}    
But, $dz/dt = H(z) (1 +z)$ and $\bar{n}^0 (1 + z)^3 = n$, so
\begin{equation}
    \frac{dn}{dt} = -3 n H(z) , \label{eq:dilution}
\end{equation}    
where we've inserted a minus sign to indicate that densities decrease with increasing time, or decreasing redshift.  The right-hand side of Equation \ref{eq:dilution} is added to Equations \ref{eq:HIIRateEquation}-\ref{eq:HeIIIRateEquation} when \texttt{CosmologicalExpansion = 1}.

We must also modify the minimum and maximum column densities for our integral tables.  To calculate what these should be for a simulation spanning the redshift interval $(z_i, z_f)$, minimum species fraction $x_{\mathrm{min}}$, and grid resolution (in proper coordinates) $dx$, do
\begin{align}
    N_{\HI}^{\mathrm{min}} & = \bar{n}_H^0 (1 + z_f)^3 x_{\mathrm{min}} dx   \\
    N_{\HI}^{\mathrm{max}} & = \bar{n}_H^0 (1 + z_i)^3 \Lbox
\end{align}

@@

%%%
%% SED studies
%%%
\section{Verifying Discrete SEDs with \texttt{rt1d}}
In \citet{Mirocha2012}, we used \texttt{rt1d} to verify new, optimally selected discrete spectral energy distributions for sources of ultraviolet and X-ray photons.  As we optimize more and more SEDs for fully 3D cosmological  radiation-hydro simulations, \texttt{rt1d} remains a quick and easy tool for verifying that the SEDs we're using are acceptable.

%%%
%% Advanced usage
%%%
\section{Advanced Usage}
In \cite{Mirocha2012}
